SSwAB-IT Phase 1 Analysis

### 2024-06-28 Jordana Hoppe/SSwAB-IT/phase_1_analysis.qmd
reference formatting

---
title: "SSwAB-IT Phase 1 Analysis"
author: "Tim Vigers"
date: "today"
date-format: long
format:
  html:
    toc: true
    toc-depth: 5
    toc-float: true
    code-fold: true
    self-contained: true
    fig-cap-location: top
    page-layout: full
    theme:
      light: flatly
      dark: darkly
editor: source
---

@@

For these agreement analyses, we reported accuracy metrics that include all samples. Accuracy is the proportion of samples where the two tests agreed (positive/positive and negative/negative). Cohen's kappa accounts for agreement between the two tests by chance, and is interpreted analogously to correlation where -1 indicates perfect disagreement and 1 indicates perfect agreement. A Cohen's kappa of NaN or NA indicates a lack of variability between the two tests.

@@

```{r results='asis'}
invisible(lapply(names(bug_list), function(b) {
  cat("\n")
  cat("##", as.character(bug_list[b]))
  cat("\n")
  cat("###", "Overall agreement")
  cat("\n")
  agreement(b)
  cat("\n")
  cat("###", "Agreement by group")
  cat("\n")
  agreement_test(b)
  cat("\n")
}))

# invisible(lapply(names(bug_list), function(b) {
#   cat("\n")
#   cat("##", as.character(bug_list[b]))
#   cat("\n")
#   cos <- paste0(b, "_cos")
#   sos <- paste0(b, "_sos")
#   d <- df[, c(cos, sos)]
#   d <- d[complete.cases(d), ]
#   colnames(d) <- c("COS", "SOS")
#   cat("\n")
#   c <- confusionMatrix(d[, "SOS"],
#     reference = d[, "COS"], positive = "Positive", mode = "everything"
#   )
#   metrics <- data.frame(c$overall)
#   cat("### 2x2 table")
#   cat("\n")
#   two_by_two <- data.frame(c$table)
#   print(gt(two_by_two))
#   cat("\n")
#   cat("### Accuracy")
#   cat("\n")
#   print(gt(metrics, rownames_to_stub = T) %>%
#     fmt_number(n_sigfig = 3) %>%
#     tab_options(column_labels.hidden = TRUE))
#   cat("\n")
#   cat("### Agreement plot")
#   cat("\n")
#   print(agreementplot(table(d)))
#   cat("\n")
#   cat("### Positive/Positive Excluded")
#   cat("\n")
#   t <- d[rowSums(d == "Positive") < 2, ]
#   t$`Samples With a Negative Test` <- paste(
#     "COS", t[, "COS"], "/", "SOS", t[, "SOS"]
#   )
#   t %>%
#     select(`Samples With a Negative Test`) %>%
#     tbl_summary() %>%
#     add_ci() %>%
#     as_gt() %>%
#     print()
#   cat("\n")
#   cat("### Euler diagram of negative results")
#   cat("\n")
#   print(plot(euler(d == "Negative"), quantities = T))
#   cat("\n")
# }))
```

>>>>

---
title: "SSwAB-IT Phase 1 Analysis"
author: "Tim Vigers"
date: "today"
date-format: long
format:
  html:
    toc: true
    toc-depth: 5
    toc-float: true
    code-fold: true
    self-contained: true
    fig-cap-location: top
    page-layout: full
    theme:
      light: flatly
      dark: darkly
bibliography: /home/timvigers/Documents/Miscellaneous/zotero.bib
csl: /home/timvigers/GitHub/styles/american-medical-association.csl
editor: source
---

@@

For these agreement analyses, we reported accuracy metrics that include all samples. Accuracy is the proportion of samples where the two tests agreed (positive/positive and negative/negative). Cohen's kappa accounts for agreement between the two tests by chance, and is interpreted analogously to correlation where -1 indicates perfect disagreement and 1 indicates perfect agreement [@mchughInterraterReliabilityKappa2012;@ranganathanCommonPitfallsStatistical2017]. A Cohen's kappa of NaN or NA indicates a lack of variability between the two tests.

@@

```{r results='asis'}
invisible(lapply(names(bug_list), function(b) {
  cat("\n")
  cat("##", as.character(bug_list[b]))
  cat("\n")
  cat("###", "Overall agreement")
  cat("\n")
  agreement(b)
  cat("\n")
  cat("###", "Agreement by group")
  cat("\n")
  agreement_test(b)
  cat("\n")
}))
```

# Sub-group comparisons
